Missing The Point

### 2020-10-16 Manuscript.Rmd
Convert to pdf

---
title: "Missing The Point"
author: "Hanne Oberman"
date: "7-9-2020"
output: html_document
bibliography: ref.bib
---

@@

Algorithm 1: simulation set-up (pseudo-code)

@@

```{r echo=FALSE}
p <- generic_plot(v="ac.max.mu.Y", name = "AC chain means")
p %>% plotly::ggplotly()
```

@@

```{r echo=FALSE}
p <- generic_plot(v="ac.max.sigma.Y", name = "AC chain variances")
p %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="ac.max.qhat", name = "AC scientific estimate")
p %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="ac.max.lambda", name = "AC novel theta")
p %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="r.hat.max.mu.Y", name = "R hat chain means")
p %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="r.hat.max.sigma.Y", name = "R hat chain variances")
p %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="r.hat.max.qhat", name = "R hat scientific estimate")
p %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="r.hat.max.lambda", name = "R hat novel theta")
p %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v = "est", name = "Bias in regression estimate") + 
  list(geom_hline(yintercept = 0, color = "grey")) 
p %>% plotly::ggplotly()
```

@@

```{r echo=FALSE}
p <- generic_plot( v ="cov", name = "Coverage rate") + 
  list(geom_hline(yintercept = 0.95, color = "grey"))
p %>% plotly::ggplotly()

@@

```{r echo=FALSE}
p <- generic_plot(v="CIW", name = "CI width") 
p %>% plotly::ggplotly()
```

@@

```{r echo=FALSE}
p <- generic_plot(v="rsq", name = "Bias in coefficient of determination") +
  list(geom_hline(yintercept = 0, color = "grey"))
p %>% plotly::ggplotly()
```

>>>>

---
title: "Missing The Point"
author: "Hanne Oberman"
date: "7-9-2020"
output:
  html_document: default
  pdf_document: default
bibliography: ref.bib
---

@@

*Algorithm 1: simulation set-up (pseudo-code)*

@@

```{r echo=FALSE}
p <- generic_plot(v="ac.max.mu.Y", name = "AC chain means")
p # %>% plotly::ggplotly()
```

@@

```{r echo=FALSE}
p <- generic_plot(v="ac.max.sigma.Y", name = "AC chain variances")
p # %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="ac.max.qhat", name = "AC scientific estimate")
p # %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="ac.max.lambda", name = "AC novel theta")
p # %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="r.hat.max.mu.Y", name = "R hat chain means")
p # %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="r.hat.max.sigma.Y", name = "R hat chain variances")
p # %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="r.hat.max.qhat", name = "R hat scientific estimate")
p # %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v="r.hat.max.lambda", name = "R hat novel theta")
p # %>% plotly::ggplotly() 
```

@@

```{r echo=FALSE}
p <- generic_plot(v = "est", name = "Bias in regression estimate") + 
  list(geom_hline(yintercept = 0, color = "grey")) 
p # %>% plotly::ggplotly()
```

@@

```{r echo=FALSE}
p <- generic_plot( v ="cov", name = "Coverage rate") + 
  list(geom_hline(yintercept = 0.95, color = "grey"))
p # %>% plotly::ggplotly()

@@

```{r echo=FALSE}
p <- generic_plot(v="CIW", name = "CI width") 
p # %>% plotly::ggplotly()
```

@@

```{r echo=FALSE}
p <- generic_plot(v="rsq", name = "Bias in coefficient of determination") +
  list(geom_hline(yintercept = 0, color = "grey"))
p # %>% plotly::ggplotly()
```
